Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-19 qpip0.tex
Auto-indent qpip0.tex
Add author note about gamma
Add question about parallel rep citation
Add more questions
Start rewriting parallel rep

%\hannote{In this section, we modify the construction of \cite{FOCS:Mahadev18a} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}

% We then extend our scheme for $\QPIP_0$ using results from \cite{FOCS:Mahadev18a}.

@@

% since Protocol~\ref{proto:urmila4} has a constant soundness error\hannote{too imprecise}\footnote{Protocol~\ref{proto:urmila4} doesn't have a formally defined soundness error. But intuitively, the verifier would accept a non-binding result will constant probability.}, Protocol~\ref{proto:qpip0_naive}  also has a constant soundness error, which means the outputted samples have constant computational distance to the ideal distribution, making the result not very useful.

%Subprotocol for Quantum Measurements
% \subsection{$\QPIP_0$ for BQP?}
% \hannote{Ethan old description before parallel rep.}
% As a warm-up, we  restate the construction in \cite{FOCS:Mahadev18a}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.

% Let $\rho$ be an $n$-qubit state. Let $h$ be an n-bits string called the \emph{basis choice}. That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead. Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.

@@

%  that : if $h_i=0$, he wants a $X$ measurement on $i$-th qubit; if $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
% At the end of $\PiMeasure$, the verifier learns a measurement outcome $M_{XZ}(\rho, h)$.

@@

% \begin{definition}
% With loss of generality,  we can assume that the testing round verification is deterministic. We denote the set of strings $a$ \Ethan{Font makes this $a$ look screwy} accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$. \hannote{do  i actually use this}
% \end{definition}

@@

% Note that in $\PiNaive$ the verifier only learns the output in the Hadamard round.
% So $\PiNaive$ is not a $\QPIP_0$ with good completeness or soundness.

@@

\subsection{$\QPIP_0$ protocol for $\SampBQP$} \label{sec:qpip0}
%Parallel Repetition of the Measurement Subprotocol

\iffalse
The following protocol is a $\QPIP_0$ protocol for $\SampBQP$

$\forall c\in\bbN$ Soundness = $O(T^{-c})$

Given inverse poly p(T), we can parameterize the protocol to have soundness p(T)
\fi

%    \label{ProtoQPIP1}

@@

@@

@@

Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string},
%\hannote{gamma..}

@@

>>>>

@@

@@

@@

@@

@@

\subsection{$\QPIP_0$ protocol for $\SampBQP$} \label{sec:qpip0}

@@

	\Ethan{Maybe $G_0$ and $G_1$ need to post-select on $in$ and $ph$ registers too?}

@@

\Ethan{Pull the definitions of $z_i$ and $z_{good, i}$ up here}

\begin{theorem}
	\Ethan{First part of main theorem this section}
	$z_i\approx z_{good, i}$
\end{theorem}

\begin{theorem}
	\Ethan{Second part of main theorem this section}
	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
	\Ethan{Need to define $d_i$ here}
\end{theorem}

\begin{theorem}
	\Ethan{TODO some kinda average argument}
\end{theorem}

@@

Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string},
\hannote{gamma..}
\Ethan{Maybe take expected value over gamma here}

@@

\Ethan{Is this particular $z_{ideal, i}$ defined? As in, what's its corresponding accept probability?}
